### 2022-11-15 NSF2022/Description/priorsupport.tex
yny 1115a

\noindent
{\it Broader impacts:} 
One PhD student (Szu-Pei Fu) was funded to work with PI Young, and work
has resulted in seven papers~\cite{Nganguia2013_PoF, Nganguia2013_PRE,
Young2014_JFM, Young2015_PoF, Nganguia2015_CiCP, Pak2015_PNAS,
fu2015pre}. 
%PI Young has been actively involved with promotion of
%underrepresented students at NJIT. One PhD student, Herve Nganguia, is
%now an Assistant Professor at Towson University. PI Young has taught a
%broad spectrum of courses in fluid mechanics and applied math modeling.

@@

\noindent
{\it Broader impacts:} 
A third-year PhD student (Jake Cherry) has been assigned to this
project. One paper has been accepted~\cite{che-lin-her-qua2022} and
another is under review~\cite{moo-che-chi-qua2022}.

@@

\begin{comment}
\begin{wrapfigure}[11]{r}{0.56\textwidth}
\vspace{-19pt}
%\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=blue},
    bar incomplete/.append style={fill=blue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
\end{ganttchart}
\vspace{-10pt}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project. The lead PI of each Specific Aim will be
  Ryham (red), Quaife (blue), and Young (green). Project management will
  be continuous (black), but we anticipate extra attention will be
  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
\label{fig:schedule}
\end{wrapfigure}
\end{comment}
PI Quaife is responsible for the overall management of the project.
The research work is structured to meet the tasks
in \S\ref{sec:proposed-work}. The PIs and students will meet
by video conference and in person when possible. PI Ryham and PI Young
will conduct biweekly meetings in person, with PI Quaife joining over
video conference from Florida. The PIs will share software packages, paper sources,
and references on a common \textsf{Git} repository. The resulting
software packages will be posted on the \textsf{Github} software
repository.
%
%\smallskip
%
The detailed schedule for the proposed work
is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a
Specific Aim, and program management will happen
throughout, with special coordination taken in quarters 4, 8, and
12.

>>>>

\noindent
{\em Broader impacts:} 
One PhD student (Szu-Pei Fu) was funded to work with PI Young, and work
has resulted in seven papers~\cite{Nganguia2013_PoF, Nganguia2013_PRE,
Young2014_JFM, Young2015_PoF, Nganguia2015_CiCP, Pak2015_PNAS,
fu2015pre}. 
%PI Young has been actively involved with promotion of
%underrepresented students at NJIT. One PhD student, Herve Nganguia, is
%now an Assistant Professor at Towson University. PI Young has taught a
%broad spectrum of courses in fluid mechanics and applied math modeling.

@@

\noindent
{\em Broader impacts:} 
A third-year PhD student (Jake Cherry) has been assigned to this
project. One paper has been accepted~\cite{che-lin-her-qua2022} and
another is under review~\cite{moo-che-chi-qua2022}.

@@

\begin{comment}
\begin{wrapfigure}[11]{r}{0.56\textwidth}
\vspace{-19pt}
%\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=blue},
    bar incomplete/.append style={fill=blue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
\end{ganttchart}
\vspace{-10pt}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project. The lead PI of each Specific Aim will be
  Ryham (red), Quaife (blue), and Young (green). Project management will
  be continuous (black), but we anticipate extra attention will be
  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
\label{fig:schedule}
\end{wrapfigure}
\end{comment}
PI Quaife is responsible for the overall management of the project.
The research work is structured to meet the tasks
in \S\ref{sec:proposed-work}. The PIs and students will meet
by video conference and in person when possible. PI Ryham and PI Young
will conduct biweekly meetings in person, with PI Quaife joining over
video conference from Florida. 
%The PIs will share software packages, paper sources,
%and references on a common \textsf{Git} repository. 
Documents and 
software will be managed and shared on \textsf{Github}.
%
%\smallskip
%
The detailed schedule for the proposed work is shown in
Figure~\ref{fig:schedule}. Each PI will spearhead a Specific Aim, and
program management will happen throughout, with special coordination
taken in quarters 4, 8, and 12.
